Clustering exploration for `r params$library_id`

### 2024-11-26 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering-metrics.Rmd

```{r}
# check that sce file exists
stopifnot(
  "sce file does not exist" = file.exists(params$sce_file)
)
```

>>>>

```{r}
# check that sce file exists
stopifnot(
  "sce file does not exist" = file.exists(params$sce_file), 
  "clustering results file does not exist" = file.exists(params$cluster_results_file)
)
```
